Recursive Neural Network Part-of-Speech Tagger

### 2013-12-21 paper/paper.tex
paper: abstract

\begin{document}
\maketitle
\begin{abstract}
  TODO: Write the abstract
\end{abstract}

@@

\subsection{Future Models}

@@

@@

TODO: Specific error examples and hypotheses.

@@

\section{Future Works}

>>>>

\begin{document}
\maketitle
\begin{abstract}
 We use recursive neural network (RNN) on part of speech task (POS). There are two models are proposed and implemented, basic RNN and Compositional Vector Tagger(CVT) RNN. The performance of basic RNN is close to the HMM model and with high probability beat it if captialization information is captured. The forever tagging time of CVT model we do not analysis. We tried some very useful neural network training trics and detailly analysis the performance of basic RNN, such as verifying the contribution of sequential information and error rates of different parts of sentence and so on.
\end{abstract}

@@

\subsection{Future Models}\label{sec:futuremodel}

@@

\paragraph{Rerank with CVG}
When we implemented and tested CVG model, the forever tagging time for each sentence stopped us from working with it. So in the future, we can use the rerank idea from Socher's SVG paper. Basically, we get top N, say 100, tagging candidates from other models, and use CVG model to get score for each sentence and rerank the candidates by these scores.

@@

@@

\section{Future Works}
Because the limited time of final projects, there are still a lot of things we want to do in the future. We mentioned some new models to try in Section \ref{sec:futuremodel}, and here are some most wanted works to do:
\begin{itemize}
\item Training and tagging the CVG model: we have mentioned the hardness of training and tagging with CVG model. In the future, we want to training a CVG model no matter how long it may takes, say several days or weeks. And implement the rerank trick mentioned  in Section \ref{sec:futuremodel}.
\item Move to GPU: We are working with torch (http://www.torch.ch), which is made by NYU people and supports GPU. So in the future, we can use GPU to speed up both traning and tagging. And Theano(http://deeplearning.net/software/theano/) can another choice, which has python interface and also GPU supporting and has very good neural networks supporting.
\end{itemize}
